---
title: "Figures and Statistical Results for An Empirical Study of 225 Years of Copyright Registrations"
author: "Rosen Z. and Schwinn R."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: 
    toc: true
  word_document: default
  html_document:
    df_print: paged
header-includes:
  - \usepackage[section]{placeins}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F,
                      error = F,
                      message = F)
```

```{r, include = F}
qload = function(..., char, repo = "http://cran.us.r-project.org"){
    if (!missing(char)) {
        new_packages <- char
    } else {
        new_packages <- as.character(match.call(expand.dots = FALSE)[[2]])
    }
    oneload = function (x){
        if(!(x %in% installed.packages(.Library))){
            install.packages(x,
                             repos = repo,
                             # dependencies = T,
                             character.only = T)
        }
    }
    invisible(sapply(new_packages, 
                     oneload))
    invisible(sapply(new_packages,
                     require, character.only = T))
}

qload(
    tidyverse,
    orcutt,
    prais,
    ggplot2,
    zoo,
    mFilter,
    openxlsx,
    broom,
    flextable,
    pander,
    huxtable,
    jtools
)

if(!file.exists("copyright_data_ready_for_analysis.xlsx")){
  source("step_1_data_prep.R")
}

df = openxlsx::read.xlsx("copyright_data_ready_for_analysis.xlsx")
rownames(df) = df$year
# formulas for main text regressions ----
t3_formulas = c("total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log ", 
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                copyright.act.1831", 
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log +
                real.gdp_log + 
                copyright.act.1831 + 
                copyright.act.1870 ",
                
                "total.registrations.post.1790_log ~
                real.registration.fee_log + 
                real.gdp_log +
                copyright.act.1831 + 
                copyright.act.1870 + 
                copyright.act.1909 ", 
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                copyright.act.1831 + 
                copyright.act.1870 + 
                copyright.act.1909 + 
                copyright.act.1976", 
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                copyright.act.1831 +
                copyright.act.1870 + 
                copyright.act.1909 + 
                copyright.act.1976 + 
                Berne.1988" ) 


t4_formulas = c("total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                copyright.act.1831",
                
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log +
                real.gdp_log + 
                copyright.act.1831 +
                total.term_log +
                total.term_log2",
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log + 
                total.term_log2" ) 

t5_formulas = c("total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log ",
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log +
                total.term_log",
                
                "total.registrations.post.1790_log ~
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log +
                total.term_log2",
                
                "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log + 
                total.term_log2 + 
                real.gdp_log.x.1909 +
                copyright.act.1909" ) 



t6_formulas = c("total.registrations.post.1790.per100k_log ~ 
                real.registration.fee_log + 
                real.gdp_log ",
                
                "total.registrations.post.1790.per100k_log ~ 
                real.registration.fee_log + 
                real.gdp_log +
                total.term_log",
                
                "total.registrations.post.1790.per100k_log ~
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log +
                total.term_log2",
                
                "total.registrations.post.1790.per100k_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log + 
                total.term_log2 + 
                real.gdp_log.x.1909 +
                copyright.act.1909" ) 


t7_formulas = c("renewals.total_log ~ 
                real.renewal.fee_log  +
                real.rec.spending_log + 
                registrations_lagged_28_log
                ",
                
                "renewals.total_log ~ 
                real.renewal.fee_log  +
                real.rec.spending_log + 
                registrations_lagged_28_log + 
                year
                ",
                
                "renewals.total_log ~ 
                real.renewal.fee_log  +
                real.rec.spending_log + 
                registrations_lagged_28_log +
                renewal.ext.1962 +
                auto.renewal.1992",
                
                "renewals.total_log ~ 
                real.renewal.fee_log  +
                real.rec.spending_log + 
                registrations_lagged_28_log +
                year +
                renewal.ext.1962 +
                auto.renewal.1992"
                )

# formulas for appendix regressions ----
tA1_formulas = c("total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log + 
                total.term_log2 + 
                real.gdp_log.x.1909 +
                copyright.act.1909") 


tA2_formulas = c("total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log + 
                total.term_log2 + 
                real.gdp_log.x.1909 +
                copyright.act.1909",
                 
                 "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                # total.term_log + 
                # total.term_log2 + 
                # real.gdp_log.x.1909 +
                copyright.act.1909 +
                copyright.act.1831 +
                copyright.act.1870 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988 +
                Bono.1998",
                 
                 "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                # total.term_log + 
                # total.term_log2 + 
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                copyright.act.1831 +
                copyright.act.1870 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988 +
                Bono.1998",
                 
                 "total.registrations.post.1790_log ~ 
                real.registration.fee_log + 
                real.gdp_log + 
                total.term_log +
                total.term_log2 +
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                copyright.act.1831 +
                copyright.act.1870 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988") 

tA3_formulas = c(
    "log(total.registrations.post.1790_log) ~
                year + 
                real.rec.spending_log +
                log.expected.life +
                real.registration.fee_log + 
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988 +
                Bono.1998")



tA4_formulas = c("registrations.class.A_log ~ 
                real.gdp_log +
                real.registration.fee_log +  
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988 +
                Bono.1998",
                 
                 "registrations.class.B_log ~ 
                real.gdp_log +
                real.registration.fee_log +
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                renewal.ext.1962
                ",
                 
                 "registrations.class.CD_log ~ 
                real.gdp_log +
                real.registration.fee_log + 
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                renewal.ext.1962
                ",
                 
                 "registrations.class.E_log ~ 
                real.gdp_log +
                real.registration.fee_log + 
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988+
                Bono.1998
                ",
                 
                 "registrations.class.GHIJK_log ~ 
                real.gdp_log +
                real.registration.fee_log + 
                real.gdp_log.x.1909 +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988+
                Bono.1998
                ",
                 
                "registrations.class.LM_log ~ 
                real.gdp_log +
                real.registration.fee_log + 
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988 +
                Bono.1998
                ") 


tA5_formulas = c(
    "log(renewals.class.A) ~
                real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988",
    
    "log(renewals.class.B) ~
               real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988",
    
    "log(renewals.class.CD) ~
               real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988",
    
    "log(renewals.class.E) ~
                real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                copyright.act.1909 +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988",
    
    "log(renewals.class.GHIJK) ~
                real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988",
    
    "log(renewals.class.LM) ~
               real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988")


    tA6_formulas =  c("renewals.total_log ~
               real.rec.spending_log +
                real.renewal.fee_log +
                registrations_lagged_28_log +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988",
                "log(renewals.total/registrations_lagged_28) ~
               real.rec.spending_log +
                real.renewal.fee_log +
                renewal.ext.1962 +
                sound.1972 +
                copyright.act.1976 +
                Berne.1988")



# functions for displaying regression results ----
make_tidy = function(x){
    x = summary(x)
    class(x) = "summary.lm"
    return(x)
} 

make_tables = function(formulas_vector = t3_formulas,
                       estimation_technique = "lm",
                       dataframe = df,
                       min_year = -Inf,
                       max_year = Inf,
                       # std.error, statistic, p.value 
                       error_format = "statistic" 
                       ){
    require(huxtable)
    
    dataframe = dataframe %>%
        filter(year > (min_year - 1), year < (max_year + 1))
    
    results = list()
    adj_R_squared = c()
    durbin_watson = c()
    
    results_string = ""
    make_tidy = function(x){
        x = summary(x)
        class(x) = "summary.lm"
        # class(x) = "lm"
        # tidy(x)
        return(x)
    }
    
    if(estimation_technique == "lm"){
        for(i in seq_along(formulas_vector)){
            results[[i]] = lm(formulas_vector[i], data = dataframe) %>% make_tidy
            results_string = paste0(c(results_string, ", results[[", i, "]]"), collapse = "") %>%
                gsub("^, ", "", .)
        }
        results_string
        table_command = paste0("the_table = huxreg(", results_string, ", error_format = '({", error_format, "})' )")
        eval(parse(text = table_command ))
    }
    
    if(estimation_technique == "prais"){
        for(i in seq_along(formulas_vector)){
            
            # runs prais-winsten analysis
            temp = prais::prais_winsten(formulas_vector[i], 
                                        data = dataframe)
            
            # calculates adjusted R squared
            y = temp$model[,1]
            y_hat = temp$fitted.values
            parameters = ncol(temp$model)-1
            N = nrow(temp$model)
            R2 = 1-(sum((y_hat - y)^2))/sum((y-mean(y))^2)
            adj_R_squared[i] = 1-(1-R2)*((N-1)/(N-(parameters)-1))
            
            # adds results to the results list
            results[[i]] = temp %>% make_tidy
            
            # retrieves durbin-watson statistic
            durbin_watson[i] = results[[i]]$dw[2]
            
            
            # adds to a string that will call the results
            results_string = paste0(c(results_string, ", results[[", i, "]]"), collapse = "") %>%
                gsub("^, ", "", .)
        }
        results_string
        table_command = paste0("the_table = huxreg(", results_string, ", error_format = '({", error_format, "})', statistics = c(N = 'nobs') )")
        eval(parse(text = table_command ))
        
        the_table = rbind(the_table[1:(nrow(the_table)-2),],
                          c("Durbin-Watson", durbin_watson),
                          c("adj. R-squared", adj_R_squared),
                          the_table[(nrow(the_table)-1):nrow(the_table),])
    }
    
    if(estimation_technique == "orcutt"){
        for(i in seq_along(formulas_vector)){
            results[[i]] = orcutt::cochrane.orcutt(lm(formulas_vector[i], data = dataframe)) %>% make_tidy
            results_string = paste0(c(results_string, ", results[[", i, "]]"), collapse = "") %>%
                gsub("^, ", "", .)
        }
        results_string
        table_command = paste0("the_table = huxreg(", results_string, ", error_format = '({", error_format, "})' )")
        eval(parse(text = table_command ))
        
        the_table
    }
    return(the_table)
}

# Sys.setenv("RSTUDIO_PANDOC" = "PATH TO PANDOC BIN")
```

# Figure 4 - Raw and Normalized Registrations 1870-2015

```{r}
library(ggthemes)
library(scales)
library(gridExtra)
dir.create("figures", showWarnings = F)
options(scipen = 99)

f_df = df  %>%
  filter(year %in% 1870:2015) %>% 
  select(year,
         original.total.registrations.post.1790,
         total.registrations.post.1790
         ) %>%
  rename(`Raw Registrations` = original.total.registrations.post.1790,
         `Normalized Registrations` = total.registrations.post.1790) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 


ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7) +
  geom_smooth() +
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  facet_wrap(~name,
             nrow = 2)

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 4 - Raw and Normalized Registrations 1870-2015.png")

```

# Figure 5 - Copyright Registrations per 100,000 People, 1790-1870 and 1870-2015

```{r}
f_df = df  %>%
  filter(year %in% 1790:1870) %>% 
  select(year,
         total.registrations.post.1790.per100k
         ) %>%
  # rename(`Raw Registrations` = original.total.registrations.post.1790,
  #        `Normalized Registrations` = total.registrations.post.1790) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 

a = ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7) +
  geom_smooth()+
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title = element_blank())

f_df = df  %>%
  filter(year %in% 1870:2015) %>% 
  select(year,
         total.registrations.post.1790.per100k
         ) %>%
  # rename(`Raw Registrations` = original.total.registrations.post.1790,
  #        `Normalized Registrations` = total.registrations.post.1790) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 

b = ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7) +
  geom_smooth()+
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) 
c = arrangeGrob(a,b)
c
ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 5 - Copyright Registrations per 100,000 People, 1790-1870 and 1870-2015.png", c)

```

<!-- # Figure 6 - Copyright Registrations per Capita by Type 1870-2012 -->

```{r}
# f_df = df %>%
#   filter(year %in% 1870:2012) %>% 
#   select(year,
#          registrations.class.A.per100k,                     
#          registrations.class.B.per100k,                     
#          registrations.class.E.per100k 
#          ) %>%
#   rename(`A: Books` = registrations.class.A.per100k,
#          `B: Periodicals` = registrations.class.B.per100k,
#          `E: Music` = registrations.class.E.per100k ) %>%
#   pivot_longer(cols = c(
#    names(.)[names(.) != 'year']
#   )) 
# f_df = f_df[f_df$value != 0, ]
# 
# a = ggplot(f_df, aes(year, value)) +
#   geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
#   geom_point(alpha = 0.7, aes(color = name, shape = name)) +
#   scale_y_continuous(labels = comma) +
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) + 
#   theme(axis.title = element_blank()) 
# 
# f_df = df %>%
#   filter(year %in% 1870:1977) %>% 
#   select(year,
#          registrations.class.CD.per100k,                     
#          registrations.class.GHIJK.per100k,                     
#          registrations.class.LM.per100k 
#          ) %>%
#   rename(`CD: Dramatic Works and Lectures` = registrations.class.CD.per100k,
#          `G--K: Graphical Works` = registrations.class.GHIJK.per100k,
#          `E: Motion Pictures` = registrations.class.LM.per100k ) %>%
#   pivot_longer(cols = c(
#    names(.)[names(.) != 'year']
#   )) 
# f_df = f_df[f_df$value != 0, ]
# 
# b = ggplot(f_df, aes(year, value))  +
#   geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
#   geom_point(alpha = 0.7, aes(color = name, shape = name)) +
#   scale_y_continuous(labels = comma) +
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) + 
#   theme(axis.title = element_blank()) + 
#   theme(legend.position="bottom",
#         legend.direction="vertical")
# grid.arrange(a,b)
# 
# ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 6 - Copyright Registrations per Capita by Type 1870-2012 (top) and 1870-1977 (bottom).png")
```

# Figure 6 - Copyright Registrations per Capita by Type 1870-2012 

```{r}


f_df = df %>%
  filter(year %in% 1870:2012) %>% 
  select(year,
         registrations.class.A.per100k,                      
         registrations.class.B.per100k,                     
         registrations.class.E.per100k,
         registrations.class.GHIJK.per100k 
         ) %>%
  rename(`A: Books` = registrations.class.A.per100k,
         `B: Periodicals` = registrations.class.B.per100k,
         `E: Music` = registrations.class.E.per100k,
         `G--K: Graphical Works` = registrations.class.GHIJK.per100k,) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 
f_df = f_df[f_df$value != 0, ]

ggplot(f_df, aes(year, value)) +
  geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
  geom_point(alpha = 0.7, aes(color = name, shape = name)) +
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title = element_blank()) + 
  theme(legend.position="bottom",
        legend.direction="vertical")

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 6 - Copyright Registrations per Capita by Type 1870-2012 (top) and 1870-1977 (bottom).png")
```

# Figure 9 - Nominal and Inflation-Adjusted Copyright Registration Fees (\$) 1790-2015

```{r}
f_df = df %>% 
  select(year,
         registration.fee,
         real.registration.fee
         ) %>%
  rename(`Registration Fee` = registration.fee,
         `Real Registration Fee` = real.registration.fee,
       ) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 
f_df = f_df[f_df$value != 0, ]

ggplot(f_df, aes(year, value)) +
  geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
  geom_point(alpha = 0.7, aes(color = name, shape = name)) +
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title = element_blank()) 

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 9 - Nominal and Inflation-Adjusted Copyright Registration Fees () 1790-2015.png")
```


# Figure 10 - Copyright Registration per Capita 1790-1870 and 1870-1909 Showing Fees

```{r}
f_df = df %>%
  filter(year %in% 1790:1870) %>% 
   select(year,
         total.registrations.post.1790.per100k,
         real.registration.fee
         ) %>%
  rename(`Real Fees` = real.registration.fee) %>%
  pivot_longer(cols = c( total.registrations.post.1790.per100k)) 

a = ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7, aes(size = `Real Fees`)) +
  geom_smooth()+
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) 

f_df = df %>%
  filter(year %in% 1870:1909) %>% 
   select(year,
         total.registrations.post.1790.per100k,
         real.registration.fee
         ) %>%
  rename(`Real Fees` = real.registration.fee) %>%
  pivot_longer(cols = c( total.registrations.post.1790.per100k)) 

b = ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7, aes(size = `Real Fees`)) +
  geom_smooth()+
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) 

c = arrangeGrob(a,b)
c

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 10 - Copyright Registration per Capita 1790-1870 and 1870-1909 Showing Fees.png",c)
```

# Figure 11 - Copyright Registration per Capita 1909-1977 Showing Fees

```{r}
f_df = df%>%
  filter(year %in% 1909:1977) %>% 
   select(year,
         total.registrations.post.1790.per100k,
         real.registration.fee
         ) %>%
  rename(`Real Fees` = real.registration.fee) %>%
  pivot_longer(cols = c( total.registrations.post.1790.per100k)) 

ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7, aes(size = `Real Fees`)) +
  geom_smooth()+
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) 


 ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 11 - Copyright Registration per Capita 1909-1977 Showing Fees.png")
```

# Figure 12 - Total Renewals per Million People

```{r}

f_df = df %>%
  filter(year %in% 1909:1990) %>%
  select(year,    
         pop,
         renewals.total
         ) %>%
  mutate(renewals_per_1m = 10^6 * renewals.total/pop) %>%
  select(year, renewals_per_1m)
  
f_df = f_df[f_df$renewals_per_1m != 0, ]

ggplot(f_df[1:83,], aes(year, renewals_per_1m)) +
  geom_path(alpha = 0.7) +
  geom_point(alpha = 0.7) +
  geom_smooth() +
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title = element_blank()) 

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 12 - Total Renewals per Million People.png")
```

<!-- # Figure 13 - Renewals by Class Filed 1909-1990 -->

```{r}
# f_df = df %>% 
#   filter(year %in% 1909:1990) %>% 
#   select(year,
#          renewals.class.A,                     
#          renewals.class.B,                     
#          renewals.class.E 
#          ) %>%
#   rename(`A: Books` = renewals.class.A,
#          `B: Periodicals` = renewals.class.B,
#          `E: Music` = renewals.class.E ) %>%
#   pivot_longer(cols = c(
#    names(.)[names(.) != 'year']
#   )) 
# f_df = f_df[f_df$value != 0, ]
# 
# a = ggplot(f_df, aes(year, value)) +
#   geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
#   geom_point(alpha = 0.7, aes(color = name, shape = name)) +
#   scale_y_continuous(labels = comma) +
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) + 
#   theme(axis.title = element_blank()) 
# 
# f_df = df %>%
#   filter(year %in% 1909:1990) %>% 
#   select(year,
#          renewals.class.CD,                     
#          renewals.class.GHIJK,                     
#          renewals.class.LM 
#          ) %>%
#   rename(`CD: Dramatic Works and Lectures` = renewals.class.CD,
#          `G--K: Graphical Works` = renewals.class.GHIJK,
#          `LM: Motion Pictures` = renewals.class.LM ) %>%
#   pivot_longer(cols = c(
#    names(.)[names(.) != 'year']
#   )) 
# f_df = f_df[f_df$value != 0, ]
# 
# b = ggplot(f_df, aes(year, value))  +
#   geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
#   geom_point(alpha = 0.7, aes(color = name, shape = name)) +
#   scale_y_continuous(labels = comma) +
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) + 
#   theme(axis.title = element_blank()) + 
#   theme(legend.position="bottom",
#         legend.direction="vertical")
# grid.arrange(a,b)
# 
# ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 13 - Renewals by Class Filed 1909-1990.png")
```

# Figure 13 - Renewals by Class Filed 1909-1990 

```{r}

f_df = df %>%
  filter(year %in% 1909:1990) %>% 
  select(year,
         renewals.class.A,                     
         renewals.class.B,                     
         renewals.class.E,
         renewals.class.LM 
         ) %>%
  rename(`A: Books` = renewals.class.A,
         `B: Periodicals` = renewals.class.B,
         `E: Music` = renewals.class.E,
         `LM: Motion Pictures` = renewals.class.LM) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 
f_df = f_df[f_df$value != 0, ]

ggplot(f_df, aes(year, value)) +
  geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
  geom_point(alpha = 0.7, aes(color = name, shape = name)) +
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title = element_blank())  + 
  theme(legend.position="bottom",
        legend.direction="vertical")

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 13 - Renewals by Class Filed 1909-1990.png")
```

# Figure 14 - Total Renewal Rate For Renewals Filed 1909-1990

```{r}
f_df = df %>%
  filter(year %in% 1909:1990) %>% 
  select(year,
         renewals.rate.total
         ) %>%
  # rename(`Raw Registrations` = original.total.registrations.post.1790,
  #        `Normalized Registrations` = total.registrations.post.1790) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 

f_df = f_df[f_df$value != 0, ]


ggplot(f_df, aes(year, value)) +
  geom_path() +
  geom_point(alpha = 0.7) +
  geom_smooth()+
  scale_y_continuous(labels = round) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title=element_text(size=12)) +
  ylab("%")+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(angle = 0))


ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 14 - Total Renewal Rate For Renewals Filed 1909-1990.png")
```

<!-- # Figure 15 - Renewal Rates by Class Renewed 1909-1990 -->

```{r}
# f_df = df %>%
#   filter(year %in% 1909:1990) %>% 
#   select(year,
#          renewals.rate.A,                     
#          renewals.rate.B,                     
#          renewals.rate.E 
#          ) %>%
#   rename(`A: Books` = renewals.rate.A,
#          `B: Periodicals` = renewals.rate.B,
#          `E: Music` = renewals.rate.E ) %>%
#   pivot_longer(cols = c(
#    names(.)[names(.) != 'year']
#   )) 
# f_df = f_df[f_df$value != 0, ]
# 
# a = ggplot(f_df, aes(year, value)) +
#   geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
#   geom_point(alpha = 0.7, aes(color = name, shape = name)) +
#   scale_y_continuous(labels = comma) +
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) + 
#   theme(axis.title = element_blank()) 
# 
# f_df = df %>%
#   filter(year %in% 1909:1990) %>% 
#   select(year,
#          renewals.rate.CD,                     
#          renewals.rate.GHIJK,                     
#          renewals.rate.LM 
#          ) %>%
#   rename(`CD: Dramatic Works and Lectures` = renewals.rate.CD,
#          `GK: Graphical Works` = renewals.rate.GHIJK,
#          `LM: Motion Pictures` = renewals.rate.LM ) %>%
#   pivot_longer(cols = c(
#    names(.)[names(.) != 'year']
#   )) 
# f_df = f_df[f_df$value != 0, ]
# 
# b = ggplot(f_df, aes(year, value))  +
#   geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
#   geom_point(alpha = 0.7, aes(color = name, shape = name)) +
#   scale_y_continuous(labels = comma) +
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) + 
#   theme(axis.title = element_blank()) + 
#   theme(legend.position="bottom",
#         legend.direction="vertical")
# grid.arrange(a,b)
# 
# ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 15 - Renewals Rates by Class Renewed 1909-1990.png")
```


# Figure 15 - Renewal Rates by Class Renewed 1909-1990 

```{r}
f_df = df %>%
  filter(year %in% 1909:1990) %>% 
  select(year,
         renewals.rate.A,                     
         renewals.rate.B,                     
         renewals.rate.E, 
         renewals.rate.CD,                     
         renewals.rate.GHIJK,
         renewals.rate.LM  
         ) %>%
  rename(`A: Books` = renewals.rate.A,
         `B: Periodicals` = renewals.rate.B,
         `E: Music` = renewals.rate.E,
         `CD: Dramatic Works and Lectures` = renewals.rate.CD,
         `G--K: Graphical Works` = renewals.rate.GHIJK,
         `LM: Motion Pictures` = renewals.rate.LM ) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  )) 
f_df = f_df[f_df$value != 0, ]

ggplot(f_df, aes(year, value)) +
  geom_path(alpha = 0.7, aes(color = name, linetype = name)) +
  geom_point(alpha = 0.7, aes(color = name, shape = name)) +
  scale_y_continuous(labels = comma) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) + 
  theme(axis.title = element_blank())  + 
  theme(legend.position="bottom",
        legend.direction="vertical")


ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 15 - Renewals Rates by Class Renewed 1909-1990.png")
```


# Figure 20 - Impact of 1909 Act on Relationship between Registrations and GDP

```{r}
# Based on the coefficients reported in Table 5, the contribution of log(gdp) to log registrations was 1.499 from 1790-1909, i.e. a 1% change in gdp was associated with a 1.499% increase in registrations. That rate fell to 0.483 in the post-1909 era.

f_df = df %>%
  select(year,
         total.registrations.post.1790_log,
         real.gdp_log) %>%
  mutate(coef = c(rep(1.499,119), rep(0.483, 107)),
         name = "contribution")

f_df$log_reg_from_gdp = f_df$coef*f_df$real.gdp_log

f_df$log_reg_from_gdp[120:226] = 13.632 + f_df$log_reg_from_gdp[120:226] 

it = f_df %>%
  select(year, real.gdp_log, log_reg_from_gdp, name) %>%
  rename(`log(real gdp)` = real.gdp_log, 
         `log(registrations associated with gdp)` = log_reg_from_gdp)

ggplot(it, aes(`log(real gdp)`,`log(registrations associated with gdp)`)) +
  geom_line() + 
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) +
  theme(axis.title=element_text(size=12)) +
  xlab("Log(Real GDP)") +
  ylab("Contribution to Log(Registrations)")+
  scale_y_continuous(labels = comma)

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 20 - Impact of 1909 Act on Relationship between Registrations and GDP.png")
```

```{r}
# # Based on the coefficients reported in Table 5, the contribution of log(gdp) to log registrations was 1.499 from 1790-1909, i.e. a 1% change in gdp was associated with a 1.499% increase in registrations. That rate fell to 0.483 in the post-1909 era.
# 
# f_df = df %>%
#   select(year,
#          total.registrations.post.1790_log,
#          real.gdp_log) %>%
#   mutate(coef = c(rep(1.499,119), rep(0.483, 107)),
#          name = "contribution")
# 
# f_df$log_reg_from_gdp = f_df$coef*f_df$real.gdp_log
# 
# f_df$log_reg_from_gdp[120:226] = 13.632 + f_df$log_reg_from_gdp[120:226] 
# 
# it = f_df %>%
#   select(year, real.gdp_log, log_reg_from_gdp, name) %>%
#   mutate(`Real GDP` = exp(real.gdp_log), 
#          `Registrations associated with GDP` = exp(log_reg_from_gdp))
# 
# ggplot(it, aes(`Real GDP`, `Registrations associated with GDP`)) +
#   geom_line() + 
#   theme_excel_new() +
#   theme(panel.grid.major.x = element_blank()) +
#   theme(axis.title = element_blank()) +
#   scale_y_continuous(labels = comma)
#   ggtitle("Response of Registrations to Real GDP")
# 
# ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 20 - Impact of 1909 Act on Relationship between Registrations and GDP.png")
```

# Figure 21 - Estimated Contribution of Total Term to Yearly Registrations

```{r}

f_df = df %>%
  select(year,
         total.term,
         total.term_log,
         total.term_log2) 

x = 1:80
y = 5.301 * (log(x)) - 0.614 * (log(x) ^ 2)
f_df = data.frame(x = x, y = exp(y))


ggplot() +
  geom_line(data = f_df, aes(x,y))+ 
  geom_text(data = data.frame(x = 75, y = 84000, note = "maximum\nat\n75 years"), aes(x,y,label = note)) + 
  theme_excel_new()  +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title=element_text(size=12)) +
  xlab("Total Term of Protection") +
  ylab("Contribution to Registrations")+
  scale_y_continuous(labels = comma)

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 21 - Estimated Contribution of Total Term to Yearly Registrations.png")
```

# Figure 22 - Predicted versus Actual log(Registrations)

```{r}
f_df = df %>%
  select(
    year,
    total.registrations.post.1790_log,
    real.registration.fee_log,
    real.gdp_log,
    total.term_log,
    total.term_log2,
    real.gdp_log.x.1909,
    copyright.act.1909
  ) %>%
  mutate(
    `Predicted log(Registrations)` =
      (-19.658) +
      (-0.063 * real.registration.fee_log) +
      (1.499 * real.gdp_log) +
      (5.301 * total.term_log) +
      (-0.614 * total.term_log2) +
      (-1.016 * real.gdp_log.x.1909) +
      (13.632 * copyright.act.1909)
  ) %>%
  rename(`Actual log(Registrations)` = total.registrations.post.1790_log) %>%
  select(year,
         `Predicted log(Registrations)`,
         `Actual log(Registrations)`) %>%
  pivot_longer(cols = c(`Predicted log(Registrations)`,
                        `Actual log(Registrations)`))

ggplot(f_df, aes(year, value)) +
  geom_line(aes(color = name, linetype = name)) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) 

ggsave(width = 5, height = 4, dpi = 600, filename = "figures/Figure 22 - Predicted versus Actual log(Registrations).png")

```



# Figure A1 - Expected Life and Depreciation Rates Based on CCEs 

```{r}
f_df = df %>%
  select(
    year,
    expected.life,
    depreciation.rate
  ) %>%
  filter(year %in% 1909:1990)
  #%>%
  # rename(`Expected Life of Copyright (years)` = expected.life,
  # `Depreciation Rate` = depreciation.rate) %>%
  # pivot_longer(cols = c(
  #  names(.)[names(.) != 'year']
  # )) 

a = ggplot(f_df, aes(year, expected.life)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  geom_smooth() +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) +
  ggtitle("Expected Life of Copyright (years)")


b = ggplot(f_df, aes(year, depreciation.rate)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  geom_smooth() +
  scale_y_continuous(labels = percent) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) +
  ggtitle("Depreciation Rate")

c = arrangeGrob(a,b)

ggsave(width = 5, height = 4, dpi = 600, 
       filename = "figures/Figure A1 - Expected Life and Depreciation Rates Based on CCEs.png", plot = c)

```

# Figure A2 - Real Recreation Spending Percent of Real GDP 

```{r}
f_df = df %>%
  select(
    year,
    rec.percent.of.gdp
  ) %>%
  filter(year %in% 1921:2012)


ggplot(f_df, aes(year, rec.percent.of.gdp)) +
  geom_line() +
  geom_point(alpha = 0.7) +
  geom_smooth() +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) +
  scale_y_continuous(labels = percent)

ggsave(width = 5, height = 4, dpi = 600, 
       filename = "figures/Figure A2 - Real Recreation Spending Percent of Real GDP.png")

```

# Figure A3 - Main Series Plots (Part 1)
```{r}
f_df = df %>%
  select(
    year,
    total.registrations.post.1870,
    registrations.class.A,
    registrations.class.B,
    registrations.class.CD,
    registrations.class.E,
    registrations.class.GHIJK,
    registrations.class.LM
  ) %>%
  filter(year %in% 1870:2015) %>%
  rename(`Total Registrations` = total.registrations.post.1870,
         `A: Books` = registrations.class.A,
         `B: Periodicals` = registrations.class.B,
         `CD: Dramatic Works and Lectures` = registrations.class.CD,
         `E: Music` = registrations.class.E,
         `G-K: Graphical Works` = registrations.class.GHIJK,
         `LM: Motion Pictures` = registrations.class.LM ) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  ))

f_df$value[f_df$value == 0] = NA

ggplot(f_df, aes(year, value)) +
  geom_line() +
  # geom_point(alpha = 0.7) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) +
  scale_y_continuous(labels = comma) +
  facet_wrap(~name,
             ncol = 1,
             scales = "free_y")

ggsave(width = 5, height = 6, dpi = 600, 
       filename = "figures/Figure A3 - Main Series Plots (Part 1).png")

```
# Figure A4 - Main Series Plots (Part 2)
```{r}
f_df = df %>%
  select(
    year,
    total.registrations.post.1870.per100k,
    real.gdp,
    total.term,
    real.registration.fee
  ) %>%
  filter(year %in% 1870:2015) %>%
  rename(`Total Registrations per Capita` = total.registrations.post.1870.per100k,
    `Real GDP ($ M)` = real.gdp,
    `Total Term of Copyright Protection (years)` = total.term,
    `Real Registration Fee ($)`= real.registration.fee) %>%
  pivot_longer(cols = c(
   names(.)[names(.) != 'year']
  ))

f_df$value[f_df$value == 0] = NA

ggplot(f_df, aes(year, value)) +
  geom_line() +
  # geom_point(alpha = 0.7) +
  theme_excel_new() +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.title = element_blank()) +
  scale_y_continuous(labels = comma) +
  facet_wrap(~name,
             ncol = 1,
             scales = "free_y")

ggsave(width = 5, height = 6, dpi = 600, 
       filename = "figures/Figure A4 - Main Series Plots (Part 2).png")

```


```{r, include = F}
t3 = make_tables(t3_formulas, estimation_technique = "prais") # Use "lm" for OLS
t4 = make_tables(t4_formulas, estimation_technique = "prais")
t5 = make_tables(t5_formulas, estimation_technique = "prais") # Or use "orcutt" for cochrane-orcutt
t6 = make_tables(t6_formulas, estimation_technique = "prais")
t7 = make_tables(t7_formulas, estimation_technique = "prais",
            min_year = 1909,
            max_year = 2006)

# Use "lm" for OLS
tA1_a = make_tables(tA1_formulas, estimation_technique = "lm") 
# Use "prais" for Prais-Watson
tA1_b = make_tables(tA1_formulas, estimation_technique = "prais") 
# Or use "orcutt" for cochrane-orcutt
tA1_c = make_tables(tA1_formulas, estimation_technique = "orcutt") 

tA2 = make_tables(tA2_formulas, estimation_technique = "prais") 

tA3_a = make_tables(tA3_formulas, estimation_technique = "lm",
                    min_year = 1911,
                    max_year = 2000)
tA3_b = make_tables(tA3_formulas, estimation_technique = "prais",
                    min_year = 1911,
                    max_year = 2000) 
tA3_c = make_tables(tA3_formulas, estimation_technique = "orcutt",
                    min_year = 1911,
                    max_year = 2000) 

tA4 = make_tables(tA4_formulas, estimation_technique = "prais",
                  min_year = 1870,
                  max_year = 2012) 

tA4_bcd = make_tables(tA4_formulas[2:3], estimation_technique = "prais",
                  min_year = 1870,
                  max_year = 1977) 

tA4_lm = make_tables(tA4_formulas[6], estimation_technique = "prais",
                  min_year = 1912,
                  max_year = 2012) 

tA5_a = make_tables(tA5_formulas[1:4], 
            estimation_technique = "prais",
            min_year = 1909,
            max_year = 1990) 
tA5_b = make_tables(tA5_formulas[5], 
            estimation_technique = "prais",
            min_year = 1915,
            max_year = 1990) 
tA5_c = make_tables(tA5_formulas[6], 
            estimation_technique = "prais",
            min_year = 1941,
            max_year = 1990)

tA6 = make_tables(tA6_formulas, 
            estimation_technique = "prais",
            min_year = 1909,
            max_year = 1990)
```

# Table 3 Log Total Copyright Registrations, 1790–2015 

```{r, results='asis'}
t3
```

# Table 4 Log Total Copyright Registrations, 1790–2015 

```{r, results='asis'}
t4
```

# Table 5 Log Total Copyright Registrations, 1790–2015 

```{r, results='asis'}
t5
```


```{r}
# years = (0:750)/10
# registrations = exp(5.452 *log(years) - 0.635 *log(years)^2)
# library(ggplot2)
# ggplot(data.frame(years, registrations),
#        aes(x = years, y = registrations))+
#     geom_line()

```

# Table 6 Log Total Copyright Registrations per 100,000 people, 1790–2015 

```{r, results='asis'}
t6
```


# Table 7 Log Renewals, 1909–2006 

```{r, results='asis'}
t7
```

# Table A1 Log Total Copyright Registrations, 1790-2015 

```{r, results='asis'}
tA1_a
tA1_b
tA1_c
```

# Table A2 Log Total Copyright Registrations with Statutory Events, 1790-2015 


```{r, results='asis'}
tA2
```

# Table A3 Landes-Posner Specification, 1910-2000 

```{r, results='asis'}
tA3_a
tA3_b
tA3_c
```

# Table A4 Registrations by Class 

## 1870 - 2012
```{r, results='asis'}
tA4
```

## 1870 - 1977

```{r}
tA4_bcd
```

## 1912 - 2012

```{r}
tA4_lm
```

# Table A5 Renewals by Class

```{r, results='asis'}
tA5_a
tA5_b
tA5_c
```

# Table A6 Renewal Rate

```{r, results='asis'}
tA6
```